\documentclass[a4paper,11pt]{letter}
\usepackage[margin=1in]{geometry}

\begin{document}
		
	\textbf{\Large RENJITH THAZHATHETHIL}\smallskip
	
	NBHM Post Doctoral fellow,\\
	Statistical and Mathematical Unit,\\
	Indian Statistical Institute, Bangalore - 560096.\smallskip
	
	\hspace*{-0.6em}\begin{tabular}{ll}
		Email&: renjitht\_pd@isibng.ac.in,\quad renjith1194@gmail.com\\
		Mobile&: +91 98470 63822,\quad +91 82810 33822
	\end{tabular}
	
	\textbf{\large Education}\smallskip\hrule
	
	\begin{itemize}
		\item \textbf{PhD} in Mathematics from Indian Institute of Science, Bangalore (2018 - 2023).

		\noindent\begin{tabular}{lll}
			Reseach Supervisor&:&Prof. A K Nandakumaran.\\
			Area of Research&:&Partial Differential Equations, Homogenization, \\
			&&Optimal Control Problems.\\
		Title of PhD Thesis&:&\parbox[t]{0.65\textwidth}{Homogenization of partial differential equations on oscillating boundary domains with $L^1$ data and optimal control problems.}		
		\end{tabular}
		
		\item \textbf{MSc} Mathematics from NSS College, Ottapalam (2015-2017).	
		
		\item \textbf{BSc} Mathematics from NSS College, Ottapalam (2012-2015). 
	\end{itemize}

	\textbf{\large Publications}\smallskip\hrule
	
	\begin{itemize}
		
		\item A K Nandakumaran, Abu Sufian, Renjith T, \textit{Homogenization of elliptic PDE with $L^1$ source term in domains with boundary having very general oscillations,}\\
		\textbf{Asymptotic Analysis.(2022)}.
		
		\item A K Nandakumaran, Abu Sufian, Renjith T, \textit{Homogenization with strong contrasting diffusivity in a circular oscillating domain with $L^1$ source term,}\\
		\textbf{Ann. Mat. Pura Appl.(2022)}.
		
		\item A K Nandakumaran, Abu Sufian, Renjith T, \textit{Homogenization of semi-linear optimal control problems on oscillating domains with matrix coefficients.}\\
		\textbf{Applied Mathematics and Optimization (2024)}.
		
		\item A K Nandakumaran, Abu Sufian, Renjith T, \textit{Semi-linear optimal control problems with strong contrasting diffusivity in rough domains.}\\
		\textbf{Ann. Mat. Pura Appl.(2025)}.
	\end{itemize}
	
	\textbf{\large Research Experiences}\smallskip\hrule
	
	\begin{itemize}
		\item Worked as a research associate in the Department of Mathematics, IISc Bangalore from 01.02.2023 to 06.12.2023.
		\item Working as NBHM Post Doctorate in the Statistical and Mathematics Unit, ISI Bangalore from 12.12.2023.
	\end{itemize}
	
	\newpage

	\textbf{\large Teaching Experiences}\smallskip\hrule
	
	\textbf{Instructor}
	\begin{itemize}
		\item \textbf{Partial Differential Equations} (M-Math Course at ISI Bangalore )
	\end{itemize}
	
	\textbf{Teaching Assistant (TA)}
	\begin{itemize}
		\item \textbf{IISc Courses}
		\begin{itemize}
			\item Analysis and Linear Algebra (UG Coursee)
			\item Ordinary Differential Equations (Int PhD Course)
			\item Partial Differential Equations (Int PhD Course)
		\end{itemize}
		\item \textbf{NPTEL Online Courses}
		\begin{itemize}
			\item Measure and Integration
			\item First Course on Partial Differential Equations (Part 1 and 2)
			\item Advanced Partial Differential Equations (Part 1 and 2)
		\end{itemize}
		\item \textbf{Workshops}
		\begin{itemize}
			\item PDE and Applications (NCM Workshop)
		\end{itemize}
	\end{itemize}
	
	\textbf{\large Awards/Achievements}\smallskip\hrule
	
	\begin{itemize}
		\item CSIR JRF Rank 61, December 2017
		\item NBHM PhD Fellowship, 2018
		\item Professor Venkatachala Iyengar Scholarship, 2022
		\begin{itemize}
			\item Awarded by Department of Mathematics, IISc Bangalore.
		\end{itemize}
		\item NBHM Post Doctoral Fellowship, June 2023
	\end{itemize}

	\textbf{\large Conferences/Workshops Attended}\smallskip\hrule

	\begin{itemize}
		\item Multiscale Analysis and Theory of Homogenization, ICTS Bangalore, 26-08-2019 to 06-09-2019.
		\item Multiscale Analysis: Thematic Lectures and Meeting(Online), ICTS Bangalore, 15-02-2021 to 19-02-2021.  
		\item International Conference on Dynamical Systems, Control and their Applications, IIT Roorkee, 01-07-2022 to 03-07-2022.
		\item Control Theory meets Theory of Homogenization, IIT Bombay, 28-02-2023 to 04-03-2023.
		\item International conference on differential equations and control problems, IIT Mandi, 15-07-2023 to 17-07-2022.
		\item International Conference on Industrial and Applied Mathematics (ICIAM) - 2023, Waseda University, Tokyo, 20-08-2023 to 25-08-2023.
		\item Workshop on Multiscale Analysis cum Conference on Differential Equations,IIT Ropar, 26-02-2024 to 02-02-2024.
		\item Discussion meeting on quatitative theory on homogenization, IIT Bombay, 17-02-2025 to 22-05-2025
	\end{itemize}
	
	
\end{document}